Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Transformed Verifiability section to use definition environment

\begin{itemize}
\item{Definition 1:} A software is verifiable if its properties can be verified
  (\cite{GhezziEtAl2003}).
\item{Definition 2:} Attributes of software that relate to the effort needed for
  validating the modified software (\cite{berander2005software}).
\item{Definition 3:}) The degree to which a system or component facilitates the
  establishment of test criteria and the performance of tests to determine
  whether those criteria have been met (\cite{IEEEStdGlossarySET1990}).
\item{Definition 4:} The degree to which a requirement is stated in terms that
  permit establishment of test criteria and performance
  (\cite{IEEEStdGlossarySET1990}).
\item{Definition 5:} Ease of performing testing on a software product or system
  (\cite{IEEEStdGlossarySET1990}).
\item{\textbf{Proposed definition}:} Combo of definitions 4 and 5 ?
\end{itemize}

@@

\subsubsection{Discussion}

@@

\begin{itemize}
\item{Definition 1:} Validatability of a software is the degree of ease in
  validating(checking) that software meets user needs.
\item{Definition 2:} Validatability means ``solving the right
  equations''~\cite[p.~23]{Roache1998}.
\oo{question about this definition}
\item{Definition 3:} The degree of ease of evaluating software products or
  system to determine whether it satisfies specified business
  requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}
  \oo{Here I tweaked the meaning of validation to suit validatability}
  \oo{Only a few resource on validatability}
\item{\textbf{Proposed definition}:} Definition 3
\end{itemize}

@@

\subsubsection{Discussion}

@@

\begin{itemize}
\item{Definition 1:} The probability that the software will operate as expected
  over a specified time interval (\cite{GhezziEtAl2003}).
\item{Definition 2:} A set of attributes that relate to the capability of
  software to maintain its level of performance under stated conditions for a
  stated period of time (\cite{berander2005software}).
\item{Definition 3:} “The capability of the software product to maintain a
  specified level of performance when used under specified conditions
  (\cite{international2001iso}).
\item{Definition 4:} Code possesses the characteristic reliability to the extent
  that it can be expected to perform its intended functions satisfactorily
  (\cite{boehm2007software})
\item{Definition 5:} A concern encompassing correctness and robustness
  (\cite{meyer1988object}).
\item{Proposed definition}
\end{itemize}

@@

\subsubsection{Discussion}

@@

\subsection{Robustness \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behavior, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\noindent \textbf{Reasoning:}

@@

\noindent \textbf{Proposed definition}

@@

IEEE Standard 610 seems to speak about this. (which is superceded?)

>>>>

\begin{defn}
  A software is verifiable if its properties can be verified
  (\cite{GhezziEtAl2003}).
\end{defn}

\begin{defn}
  Attributes of software that relate to the effort needed for validating the
  modified software (\cite{berander2005software}).
\end{defn}

\begin{defn}
  The degree to which a system or component facilitates the establishment of
  test criteria and the performance of tests to determine whether those criteria
  have been met (\cite{IEEEStdGlossarySET1990}).
\end{defn}

\begin{defn}
  The degree to which a requirement is stated in terms that permit establishment
  of test criteria and performance (\cite{IEEEStdGlossarySET1990}).
\end{defn}

\begin{defn}
  Ease of performing testing on a software product or system
  (\cite{IEEEStdGlossarySET1990}).
\end{defn}

@@

Combo of definitions 4 and 5 ?

@@

\begin{itemize}
\item{Definition 1:} Validatability of a software is the degree of ease in
  validating(checking) that software meets user needs.
\item{Definition 2:} Validatability means ``solving the right
  equations''~\cite[p.~23]{Roache1998}.
\oo{question about this definition}
\item{Definition 3:} The degree of ease of evaluating software products or
  system to determine whether it satisfies specified business
  requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}
  \oo{Here I tweaked the meaning of validation to suit validatability}
  \oo{Only a few resource on validatability}
\end{itemize}

@@

Definition 3

@@

\begin{itemize}
\item{Definition 1:} The probability that the software will operate as expected
  over a specified time interval (\cite{GhezziEtAl2003}).
\item{Definition 2:} A set of attributes that relate to the capability of
  software to maintain its level of performance under stated conditions for a
  stated period of time (\cite{berander2005software}).
\item{Definition 3:} “The capability of the software product to maintain a
  specified level of performance when used under specified conditions
  (\cite{international2001iso}).
\item{Definition 4:} Code possesses the characteristic reliability to the extent
  that it can be expected to perform its intended functions satisfactorily
  (\cite{boehm2007software})
\item{Definition 5:} A concern encompassing correctness and robustness
  (\cite{meyer1988object}).
\end{itemize}

@@

@@

\subsection{Robustness \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behaviour, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

@@

@@

@@

IEEE Standard 610 seems to speak about this. (which is superseded?)
